Mapping mutational effects along the evolutionary landscape of HIV envelope

### 2017-12-15 paper/manuscript_Hugh.tex
Minor tweak to one of Hugh's comments

\begin{figure}
\begin{minipage}[t]{0.34\textwidth}
{\bf \Large A} \\ 
\centerline{{\includegraphics[clip=true, trim=4.3in 1.4in 0in 0.48in, width=0.4\textwidth]{figures/BG505_avgmutfreqs.pdf}}} 
\centerline{\small BG505}
\includegraphics[clip=true, trim=0in 0in 1.7in 0in, width=\textwidth]{figures/BG505_avgmutfreqs.pdf}
\centerline{\small BF520}
\includegraphics[clip=true, trim=0in 0in 1.7in 0in, width=0.89\textwidth]{figures/BF520_avgmutfreqs.pdf}
\end{minipage}
\begin{minipage}[t]{0.01\textwidth}
\end{minipage}
\begin{minipage}[t]{0.65\textwidth}
{\bf \Large B} \\
\includegraphics[width=\textwidth]{figures/allprefscorr.pdf}
\end{minipage}
\caption{\label{fig:mutfreqs}
The deep mutational scanning selects for functional Envs and yields measurements that are well correlated among replicates.
{\bf (A)}
The average per-codon mutation frequency when sequencing plasmids encoding wildtype Env (\emph{DNA}), plasmid mutant libraries (\emph{mutDNA}), mutant viruses after the final infection (\emph{mutvirus}), and virus generated from wildtype plasmids (\emph{virus}).
Mutations are categorized as nonsynonymous, synonymous, or stop codon. 
The \emph{DNA} samples show that sequencing errors are rare, and the \emph{virus} samples show that viral-replication errors are well below the frequency of mutations in the \emph{mutDNA} samples.
\hhaddox{I would say that reverse-transcription errors fall under the category of viral-replication errors.}
Comparing the \emph{mutvirus} to \emph{mutDNA} shows clear purifying selection against stop codons and some nonsynonymous mutations, particularly after subtracting the background error rates given by the \emph{virus} and \emph{DNA} samples (Figure~\ref{fig:mutfreqs}-Figure~supplement~\ref{figsupp:mutfreqs}).
More extensive plots from the analysis of the deep sequencing data are in Supplementary~files~\ref{suppfile:code} and \ref{suppfile:html}.
{\bf (B)}
Correlations between replicates in the measured preferences of each site in Env for all 20 amino acids.
Blue indicates replicate measurements on BF520, red indicates replicate measurements on BG505, and gray indicates across-Env measurements of BF520 versus BG505.
$R$ is the Pearson correlation coefficient. 
The numerical values for the preferences are in Figure~\ref{fig:mutfreqs}-source~data~\ref{figdata:allprefs}.
}
\figsupp[\label{figsupp:mutfreqs} Numerical frequencies of mutations.]
{This table gives the average frequencies of nonsynonymous, synonymous, and stop-codon mutations as plotted in Figure~\ref{fig:mutfreqs}.
Note that there is only one \emph{DNA} sample for BF520, so that same sample is repeated three times in the sample in conjunction with each BF520 replicate.
We calculate the error-corrected \emph{pre}-selection mutation frequency as the \emph{mutDNA} frequency minus the \emph{DNA} frequency, and the error-corrected \emph{post}-selection mutation frequency as the \emph{mutvirus} frequency minus the \emph{virus} frequency.
We then use these error-corrected frequencies to calculate the \emph{percent} of mutations remaining after selection for each replicate and type of mutation.}
{\input{figures/avgmutfreqs}}
\figdata{\label{figdata:allprefs} Preferences for each replicate and averages are in \texttt{all\_prefs\_unscaled.zip}.}
\end{figure}

>>>>

\begin{figure}
\begin{minipage}[t]{0.34\textwidth}
{\bf \Large A} \\ 
\centerline{{\includegraphics[clip=true, trim=4.3in 1.4in 0in 0.48in, width=0.4\textwidth]{figures/BG505_avgmutfreqs.pdf}}} 
\centerline{\small BG505}
\includegraphics[clip=true, trim=0in 0in 1.7in 0in, width=\textwidth]{figures/BG505_avgmutfreqs.pdf}
\centerline{\small BF520}
\includegraphics[clip=true, trim=0in 0in 1.7in 0in, width=0.89\textwidth]{figures/BF520_avgmutfreqs.pdf}
\end{minipage}
\begin{minipage}[t]{0.01\textwidth}
\end{minipage}
\begin{minipage}[t]{0.65\textwidth}
{\bf \Large B} \\
\includegraphics[width=\textwidth]{figures/allprefscorr.pdf}
\end{minipage}
\caption{\label{fig:mutfreqs}
The deep mutational scanning selects for functional Envs and yields measurements that are well correlated among replicates.
{\bf (A)}
The average per-codon mutation frequency when sequencing plasmids encoding wildtype Env (\emph{DNA}), plasmid mutant libraries (\emph{mutDNA}), mutant viruses after the final infection (\emph{mutvirus}), and virus generated from wildtype plasmids (\emph{virus}).
Mutations are categorized as nonsynonymous, synonymous, or stop codon. 
The \emph{DNA} samples show that sequencing errors are rare, and the \emph{virus} samples show that viral-replication errors are well below the frequency of mutations in the \emph{mutDNA} samples.
\hhcomment{I would say that reverse-transcription errors fall under the category of viral-replication errors.}
Comparing the \emph{mutvirus} to \emph{mutDNA} shows clear purifying selection against stop codons and some nonsynonymous mutations, particularly after subtracting the background error rates given by the \emph{virus} and \emph{DNA} samples (Figure~\ref{fig:mutfreqs}-Figure~supplement~\ref{figsupp:mutfreqs}).
More extensive plots from the analysis of the deep sequencing data are in Supplementary~files~\ref{suppfile:code} and \ref{suppfile:html}.
{\bf (B)}
Correlations between replicates in the measured preferences of each site in Env for all 20 amino acids.
Blue indicates replicate measurements on BF520, red indicates replicate measurements on BG505, and gray indicates across-Env measurements of BF520 versus BG505.
$R$ is the Pearson correlation coefficient. 
The numerical values for the preferences are in Figure~\ref{fig:mutfreqs}-source~data~\ref{figdata:allprefs}.
}
\figsupp[\label{figsupp:mutfreqs} Numerical frequencies of mutations.]
{This table gives the average frequencies of nonsynonymous, synonymous, and stop-codon mutations as plotted in Figure~\ref{fig:mutfreqs}.
Note that there is only one \emph{DNA} sample for BF520, so that same sample is repeated three times in the sample in conjunction with each BF520 replicate.
We calculate the error-corrected \emph{pre}-selection mutation frequency as the \emph{mutDNA} frequency minus the \emph{DNA} frequency, and the error-corrected \emph{post}-selection mutation frequency as the \emph{mutvirus} frequency minus the \emph{virus} frequency.
We then use these error-corrected frequencies to calculate the \emph{percent} of mutations remaining after selection for each replicate and type of mutation.}
{\input{figures/avgmutfreqs}}
\figdata{\label{figdata:allprefs} Preferences for each replicate and averages are in \texttt{all\_prefs\_unscaled.zip}.}
\end{figure}
